Supporting Information

### 2018-04-09 SupportingInformation.Rmd

Plotting Spearman or Kendall correlations between time series for pairs of locations as a function of great circle distance
between the locations (Figure \ref{fig_pns} A, B) showed the typical decline of correlation with increasing
distance. Plotting $\cor_l$ , $\cor_u$ , $\Ps_l$, and $\Ps_u$ against distances between pairs of locations shows these quantities also appear to decline with distance (Figure \ref{fig_pns} C-F). $\Dsq_u$ and $\Dsq_l$ appear to increase with distance, as expected given
their opposite meaning (Figure \ref{fig_pns} G-H). Plotting $\cor_l - \cor_u$, $\Ps_l - \Ps_u$, and $\Dsq_u - \Dsq_l$ against distance (Figure \ref{fig_pns} I-K) did not show a decline with distance, but did demonstrate visuaally the 
statistical result of Table \ref{tab_pns_resamp} that averages of these 
quantities across all pairs of sampling locations were significantly greater 
than zero, showing asymmetry of tail dependence.

\begin{figure}[!h]
\textbf{ \hspace{2.6 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.8 cm} (D)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Spearman_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Kendall_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{2.6 cm} (E) \hspace{3.6 cm} (F) \hspace{3.8 cm} (G) \hspace{3.8 cm} (H)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{4.8 cm} (I) \hspace{3.8 cm} (J) \hspace{4 cm} (K) } \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl-Coru_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl-Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for *Ceratium furca* abundance data plotted against geographical distance $(D)$ between two sampling locations. (A) Spearman correlation vs. $D$, (B) Kendall correlation vs. $D$, (C) $\cor_l$ vs. $D$, (D) $\cor_u$ vs. $D$; (E) $\Ps_l$ vs. $D$; (F) $\Ps_u$ vs. $D$; (G) $\Dsq_u$ vs. $D$; (H) $\Dsq_l$ vs. $D$; (I) $\cor_l-\cor_u$ vs. $D$; (J) $\Ps_l-\Ps_u$ vs. $D$; (K) $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all pairs of locations. \label{fig_pns}}
\end{center}
\end{figure}

>>>>

Plotting Spearman or Kendall correlations between time series for pairs of locations as a function of great circle distance
between the locations (Figure \ref{fig_pns} A, B) showed the typical decline of correlation with increasing
distance. Plotting $\cor_l$ , $\cor_u$ , $\Ps_l$, and $\Ps_u$ against distances between pairs of locations shows these quantities also appear to decline with distance (Figure \ref{fig_pns} C-F). $\Dsq_u$ and $\Dsq_l$ appear to increase with distance, as expected given
their opposite meaning (Figure \ref{fig_pns} G-H). Plotting $\cor_l - \cor_u$, $\Ps_l - \Ps_u$, and $\Dsq_u - \Dsq_l$ against distance (Figure \ref{fig_pns} I-K) did not show a decline with distance, but did demonstrate visually the 
statistical result of Table \ref{tab_pns_resamp} that averages of these 
quantities across all pairs of sampling locations were significantly greater 
than zero, showing asymmetry of tail dependence.

\begin{figure}[!h]
\textbf{ \hspace{2.6 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.8 cm} (D)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Spearman_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Kendall_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{2.6 cm} (E) \hspace{3.6 cm} (F) \hspace{3.8 cm} (G) \hspace{3.8 cm} (H)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{4.8 cm} (I) \hspace{3.8 cm} (J) \hspace{4 cm} (K) } \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl-Coru_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl-Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for \textit{Ceratium furca} abundance data plotted against geographical distance $(D)$ between two sampling locations. (A) Spearman correlation vs. $D$, (B) Kendall correlation vs. $D$, (C) $\cor_l$ vs. $D$, (D) $\cor_u$ vs. $D$; (E) $\Ps_l$ vs. $D$; (F) $\Ps_u$ vs. $D$; (G) $\Dsq_u$ vs. $D$; (H) $\Dsq_l$ vs. $D$; (I) $\cor_l-\cor_u$ vs. $D$; (J) $\Ps_l-\Ps_u$ vs. $D$; (K) $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all pairs of locations. \label{fig_pns}}
\end{center}
\end{figure}
